Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-28 paper/paper-mainfile.tex
Conny panda results

\begin{table}
	\centering
	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexCoverage}.
	\scalebox{0.7} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
\cmidrule(lr){2-3} \cmidrule(lr){4-5}   
			&PO & TO & PO & TO \\
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ.$^{2}$   \\ 
			Monroe Part. Observ.$^{2}$  \\ 
			PCP$^{17}$  \\ 
			Rover  \\ 
			Satellite   \\  
			Transport   \\ 
			UM-Translog$^{1}$  \\ 
			Woodworking$^{2}$  \\ 
			\midrule 
			Monroe   \\ 
			SmartPhone$^{1}$   \\ 
			Zenotravel   \\ 
			\midrule 
			Coverage  \\ 
			Norm. coverage  \\ 
			\bottomrule 
		\end{tabular}  
	}
\end{table}

\begin{table}
	\centering
	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexIPC}.
	\scalebox{0.7} {
		\begin{tabular}{lccccccccccccccccl} 
			\toprule 
	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
 &PO & TO & PO & TO \\
\midrule 
Barman-BDI  \\ 
Monroe Fully Observ.$^{2}$   \\ 
Monroe Part. Observ.$^{2}$  \\ 
PCP$^{17}$  \\ 
Rover  \\ 
Satellite   \\  
Transport   \\ 
UM-Translog$^{1}$  \\ 
Woodworking$^{2}$  \\ 
\midrule 
Monroe   \\ 
SmartPhone$^{1}$   \\ 
Zenotravel   \\ 
\midrule 
IPC score \\
\bottomrule 
\end{tabular}  
	}
\end{table}

>>>>

\begin{table}
	\centering
	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexCoverage}.
	\scalebox{0.7} {

\begin{tabular}{lccccccl} 
	\toprule 
	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO &PO & TO  \\ 
	\midrule 
	Barman-BDI & 5.0 & \textbf{13.0} & 4.0 & \textbf{11.0}  \\ 
	Monroe Fully Observ.$^{5}$ & \textbf{25.0} & \textbf{25.0} & \textbf{22.0} & \textbf{22.0}  \\ 
	Monroe Part. Observ. & \textbf{14.0} & 13.0 & \textbf{14.0} & \textbf{14.0}  \\ 
	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{15.0} & \textbf{15.0}  \\ 
	Rover & 10.0 & \textbf{18.0} & 4.0 & \textbf{17.0}  \\ 
	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}  \\ 
	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}  \\ 
	Woodworking$^{1}$ & 13.0 & \textbf{20.0} & 12.0 & \textbf{19.0}  \\

	\midrule 
	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
	SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{7.0}  \\ 
	Zenotravel$^{2}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\

		\midrule 
	Coverage & 245.0 & \textbf{290.0} & 233.0 & \textbf{271.0}  \\ 
	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
	\bottomrule 
\end{tabular} 
	}
\end{table}

\begin{table}
	\centering
	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexIPC}.
	\scalebox{0.7} { 
\begin{tabular}{lccccccl} 
			\toprule 
		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO  &PO & TO  \\ 
	\midrule 
	Barman-BDI & 0.09 & \textbf{0.34} & 0.06 & \textbf{0.34}  \\

	Monroe Fully Observ.$^{5}$ & \textbf{0.57} & 0.18 & \textbf{0.47} & 0.16  \\ 
	Monroe Part. Observ. & \textbf{0.31} & 0.1 & \textbf{0.31} & 0.11  \\ 
	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.83} & \textbf{0.83}  \\ 
	Rover & 0.41 & \textbf{0.84} & 0.2 & \textbf{0.69}  \\ 
	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\ 
	Transport & 0.24 & \textbf{0.65} & 0.27 & \textbf{0.31}  \\ 
	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
	Woodworking$^{1}$ & 0.38 & \textbf{0.57} & 0.35 & \textbf{0.54}  \\ 
	\midrule 
	Monroe & \textbf{0.77} & 0.48 & \textbf{0.75} & 0.48  \\ 
	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.87}  \\ 
	Zenotravel$^{2}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
		\midrule 
	IPC score & 7.2 & \textbf{8.0} & 7.0 & \textbf{7.3}  \\ 
	\bottomrule 
\end{tabular}  
	}
\end{table}
